% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{The \java{static} Keyword and Inheritance}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Today, we look at when and how to use the \java{static} keyword in Java. 
We then examine \emph{inheritance}, one of the pillars of object-oriented design.  
\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can differentiate between static and instance variables and methods. 
    \item I can summarize best practices for when to use static variables and methods. 
    \item I can explain what it means for one class to extend another 
        and summarize the \java{extends} and \java{super} keywords. 
    \item I can generalize multiple classes that have overlapping code.
    \item I can explain the requirements of abstract classes and methods. 
    \item I can write a new method for an existing Java library class. 
}{
    \item Reading Java API documentation and making inferences. (Information Processing)
	\item Making conclusions based on IDE hints and program output. (Critical Thinking)
	%\item Identifying similarities and differences between classes and refactoring to use an appropriate superclass. (Critical Thinking)
}{
\textbf{First Hour:}
\ref{static.tex} introduces static fields and methods through examples. 
Be sure to summarize best practices at the end: 
only use static fields for constants (until later courses), and 
only use static methods for utility functions and \java{main}. 

End the first hour with a 10-minute mini lecture that shows 
how to create and add two BigIntegers, and how to find and replace strings. 

\textbf{Second Hour:} 
\ref{extending.tex} introduces inheritance with a custom extension of \java{BigInteger}. 
This activity requires some prior knowledge of BigInteger and the \java{String.replace()} method. 
BigInteger was originally chosen for this activity, because (1) it's a useful class in the Java library, and (2) it's not declared as \java{final} (so it can be extended).
The new feature this activity is adding to BigInteger is the ability to work with comma separators.
% Highlight important aspects of the documentation for BigInteger.
Mention that BigInteger extends Number, which extends Object. 
Notice the static constants. 
% In addition to the constructors, there is a static \java{valueOf} method. 
Prevent students from spending too much time on \ref{count1} and \ref{count2}. 
% You can tell them the number of methods; they should be able to count the fields and constructors. 
% Introduce ``is a'' and ``has a'' terminology when reporting out. 

\ref{abstract.tex} introduces abstract superclasses. 
% Do not provide \textit{LoudToy.java} (the code for Model 2) until after Model 1.
% Students will develop their own version of this class in \ref{LoudToyV1} and later compare it with Model 2.

% \ref{refactoring-inheritance.tex} demonstrates refactoring to use an abstract class 
% in the ongoing Animal Shelter example project. 

Key questions: 
\ref{staticPatterns}, 
\ref{key1}, \ref{key2}, \ref{key3}, 
\ref{abstractKey1}, \ref{abstractKey2}
% \ref{removeAnimal}, 
% \ref{bookMainDiffs}, 
% \ref{functionalButBad}, 
% \ref{encapsAnalogy}, 
% \ref{pizza}

Source files: 
\src{Act08}{Point.java},  
\src{Act08}{MyBigInt.java},  
\src{Act08}{LoudToy.java}, 
\src{Act08}{ToySheep.java}, 
\src{Act08}{ToyRobot.java}, 
\src{Act08}{StudentV1[/V2].java}
}

\input{static.tex}
\newpage
\input{extending.tex}
\newpage
\input{abstract.tex}

\end{document}
