% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Designing Objects}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Today, we look at how to create and apply custom object types in Java. 
We will also see a useful data structure called a HashMap.

\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can explain the purpose of constructor, accessor, and mutator methods. 
    \item I can implement the equals and toString methods for a given class design. 
    \item I can design a new class (UML diagram) based on a general description. 
    \item I can explain what a HashMap represents. 
    \item I can list and apply essential HashMap operations. 
    \item I can describe the benefits and limitations of HashMaps. 
}{
    \item Identifying attributes and data types that model a real-world object. (Problem Solving)
}{
\ref{common-methods.tex} begins with questions about constructors, getters, and setters.
Report out as soon as the majority of teams have finished. 
You may find it helpful to project the source code for \textit{Color.java} 
while students work through the questions. 
Reinforce the concept of immutable objects, 
and point out that the \java{String} class is designed this way. 

The questions at the beginning of \ref{equals-tostring.tex} 
require students to understand the source code of \java{equals} and \java{toString}. 
If this is the first time they have seen language features like \java{Object}, 
\texttt{instanceof}, and \java{String.format}, 
you might want to give a 5-minute lecture (but avoid giving away the answers). 

When reporting out \ref{animal.tex}, have presenters write their designs on the board. 
Compare the trade-offs of their different designs.
For example, to store ID numbers some teams may use strings, others may use ints/longs/arrays of ints. 

\ref{maps.tex} introduces HashMaps in the context of the Animal Shelter example. 

Key questions: \ref{key1}, \ref{key2}, \ref{key3}, \ref{mapRefactor}

Source files: 
\src{Act05}{Color.java}, 
\src{Act05}{Point.java}, 
\src{Act05}{AnimalShelterMain.java}
}

\input{common-methods.tex}
\newpage
\input{equals-tostring.tex}
\vspace{1em}
\input{animal.tex}
\newpage
\input{maps.tex}

\end{document}
