% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Software Engineering Techniques}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

What makes software ``good''? 
Today, we start building some guidelines, 
object-oriented design principles (OODPs), 
that will help us quickly plan software systems 
with desirable qualities and rule out designs 
that are likely to cause us (or our teammates, or worse, our clients) 
frustration in the future. 

\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can list several attributes that make software ``good''. 
    \item I can draw a UML class diagram representing given Java classes. 
    \item I can create stubs of Java classes from a given UML class diagram. 
    \item I can use the PlantUML service to create simple UML class diagrams. 
    \item I can apply object-oriented design principles (OODPs) 1 and 2 to evaluate design options. 
    \item I can improve candidate designs by fixing flaws with respect to OODPs 1 and 2. 
}{
    \item Communicating object-oriented design ideas to team members 
          using precise language and diagrams. (Communication)
    \item Reading system requirements descriptions and extracting key information 
          for object-oriented design. (Information Processing)
    \item Building consensus from different design ideas and 
          including all team members in design discussions. (Teamwork)
}{
\ref{design-good-software.tex} introduces software design principles 
and motivates UML class diagrams. 

\ref{oodp1-oodp2.tex} defines the first two object-oriented design principles 
and walks through the Book Tracker design problem. 

\ref{design-practice.tex} structures additional practice design problems: 
Company Accounts and Card Game. 

Key questions: 
\ref{key1}, 
\ref{key2}, 
\ref{key3}, 
\ref{key4}, 
\ref{key5}

% Source files: None
% \src{Act05}{ConsoleInputMain.java},  
% \src{Act05}{Animal.java},
% \src{Act05}{AnimalShelterMain.java}, 
% \src{Act05}{BookMain.java}, 
% \src{Act05}{Book.java}, 
% \src{Act05}{Kid.java}
}

\input{design-good-software.tex}
% \newpage
\input{oodp1-oodp2.tex}
\newpage
\input{design-practice.tex}

\end{document}
