% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{OODP 4: Minimize Dependencies}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Today, we look at our fourth object-oriented design principle: 
\textbf{Minimize Dependencies}. 
We not only want to reduce the \emph{number} of dependencies between our classes, 
but also desire to decrease the \emph{strength} of the dependencies which 
we cannot remove without breaking functionality. 
Through several examples, we will see how and why to minimize dependencies. 

\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can identify and categorize dependencies between classes in both UML and code. 
    \item I can explain the design goals of ``tell, don't ask'' and ``avoid message chains''. 
    \item I can define coupling and cohesion in my own words. 
    \item I can distinguish cohesion from encapsulation. 
    \item I can apply coupling and cohesion to analyze the level and quality of dependencies in a UML design or code. 
}{
    \item Writing with technical detail using precise object-oriented design terminology. (Communication)
	\item Interpreting UML diagrams and imagining possible implementations. (Information Processing)
}{
\textbf{First Hour:}
\ref{tell-dont-ask.tex} introduces dependencies (in UML) and 
the ``Tell, Don't Ask'' design principle. 

End the first hour with a 10-minute mini lecture that shows 
the difference between telling and asking for computing game revenue 
in the Vapor Sales Manager implementation assignment. 

\textbf{Second Hour:} 
\ref{avoid-message-chains.tex} TODO

\ref{coupling-cohesion.tex} TODO

Key questions: 
\ref{tellVsAsk}, 
\ref{redFlags}, 
\ref{elimMsgChain}, 
% \ref{staticPatterns}, 
% \ref{key1}, \ref{key2}, \ref{key3}, 
% \ref{abstractKey1}, \ref{abstractKey2}
% \ref{removeAnimal}, 
% \ref{bookMainDiffs}, 
% \ref{functionalButBad}, 
% \ref{encapsAnalogy}, 
% \ref{pizza}

Source files: 
% \src{Act08}{Point.java},  
% \src{Act08}{MyBigInt.java},  
% \src{Act08}{LoudToy.java}, 
% \src{Act08}{ToySheep.java}, 
% \src{Act08}{ToyRobot.java}, 
% \src{Act08}{StudentV1[/V2].java}
}

\input{tell-dont-ask.tex}
% \newpage
\input{avoid-message-chains.tex}
\newpage
\input{coupling-cohesion.tex}

\end{document}
