% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Introduction to Objects and Debugging}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Today, we look at how to create and apply custom object types in Java. 

\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can define objects and related terms, such as field, attribute, method, constructor. 
    \item I can identify the fields and methods of a Java object. 
    \item I can create new object types in Java. 
    \item Given a Java class, I can construct the corresponding UML class diagram. 
    \item Given a UML class diagram, I can write the corresponding Java code. 
    \item I can use debugging tools. 
}{
    \item Verifying program behavior by tracing code with a debugger. (Critical Thinking)
}{
The meta activity is ultimately about process skills and should help with student buy-in. 
If you are using the \github{Handouts/role-cards-mayfield.pdf}{Role Cards}, have students look at the definitions on the reverse side. 
Each activity targets specific ``process skill goals'' from these categories. 
Point out that ``Technical skills'' and ``Leadership'' are probably ranked lower than expected. 

In~\ref{die-class.tex}, students analyze a given Java class representing a six-sided die. 

\ref{circle-class.tex} introduces UML class diagrams and how to translate them into code. 

\ref{debugging.tex} introduces the why/what/how of the debugger and ends with debugging practice. 

Key questions: 
\ref{dievar}, \ref{circmain}, \ref{debugOptions}

Source files:
\src{Act04}{Die.java}, 
\src{Act04}{debugger/DebugMe.java}, 
\src{Act04}{debugger/DebugMeTest.java}, 
\src{Act04}{debugger/WhackABug.java}
}

\input{../Meta/employers.tex}
\newpage
\input{die-class.tex} % Replaces BankAccount example
\newpage
\input{circle-class.tex} % Replaces RoseString and SmallClassProbs
\newpage
\input{debugging.tex} % Based on DebugMe and WhackABug

\end{document}
