% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Unit Testing and Test-Driven Development}
\author{Ian Ludden}
\date{Summer 2025}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Today, we start with unit testing, 
the practice of using small input/expected output pairs 
to make sure each part of our code works as intended. 
We then look at a broader software development process 
called test-driven development (TDD) 
and see how genAI tools can be leveraged in TDD. 

\ifdefined\Student\rolenames{}\fi

\guide{
    \item I can explain the benefits of using testing frameworks 
        such as JUnit over manually calling methods and printing results. 
    \item I can construct appropriate, high-quality unit tests 
        for small software systems. 
    \item I can describe the test-driven development (TDD) framework, 
        compare it with alternatives, and discuss its strengths and weaknesses. 
    \item I can integrate genAI code generation tools with TDD and 
        evaluate the resulting implementations with respect to 
        object-oriented design principles. 
}{
    \item Identifying good, thorough test cases for writing unit tests. (Problem Solving)
}{
TODO: facilitator notes
\textbf{First hour, before quiz:}
\ref{unit-testing.tex} introduces and motivates JUnit tests 
using a simple rectangle example class. 
\ref{create-tests.tex} provides guidelines for creating unit tests 
and walks through the JUnit creation process for the BadFrac example. 

\textbf{Second hour:}~%
\ref{tdd.tex} introduces the test-driven development (TDD) framework, 
and~\ref{tdd-genai.tex} explores genAI-assisted TDD. 

Key questions: 
\ref{whyUnitTests}, 
\ref{reviewTests}, 
\ref{critiqueTDD}, 
\ref{genAITestCases}

Source files: 
\src{Act10}{rectangle/BasicRectangle.java},
\src{Act10}{rectangle/BasicRectangleTest.java},
\src{Act10}{badFrac/BadFrac.java}
}

\input{unit-testing.tex}
\newpage
\input{create-tests.tex}
\newpage
\input{tdd.tex}
\newpage
\input{tdd-genai.tex}

\end{document}
